### 2015-01-30 cav-2015-tex/abstract.tex
New abstract

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  These techniques however, exacerbate the path explosion
problem.  In this work, we present a summary heap approach which takes
inspiration from the static analysis domain and defines a bipartite
graph to encode multiple heaps in single representation, which, unlike
state-of-the-art static analysis approaches, (i) supports aliasing,
(ii) does not require rewrite of constraints on heap updates, and
(iii) can initialize the heap-on-the-fly. We also define a summary
heap algorithm to perform heap updates during symbolic execution on
this representation in order to mitigate the path explosion problem in
GSE techniques. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder framework shows the summary heap
enables the initialization of larger, more complex heaps than
previously possible.

>>>>

A fundamental challenge of using symbolic execution for software
analysis is the treatment of dynamically allocated data. Existing
static analysis techniques over-approximate the potential heaps,
dynamic symbolic execution techniques often under-approximate the
heaps, while generalized symbolic execution leads to excessive
case-splitting. This paper introduces a compact heap representation
along with heap update rules that (i) allow reads and writes of
symbolic references, (ii) does not require constraint rewriting, and
(iii) supports arbitrary recursive data structures. As such, the
representation and update rules capture all possible heaps that follow
a common execution path. More importantly, in contrast to
state-of-the-art techniques, the definition and update rules are
unconstrained and not subject to bounds such as the number of heap
locations, aliasing, or memory partitions. An evaluation of a
proof-of-concept implementation in the Java Pathfinder framework is
presented to demonstrate the computational feasibility of the approach
over several classical symbolic execution benchmarks.
